---
title: "Getting Started with binomial"
author: "Dominic Fannjiang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Working with the binomial distribution

The package `"binomial"` is a minimal implementation for representing a binomial distribution and computing basic statistics and other information about it.


### Creating a binomial random variable.

You can create an object of class `binvar` that represents a binomial distribution by storing the 2 parameters needed (number of trials and chance of success) to define a binomial distribution:
```{r}
x <- bin_variable(5, 0.5)
c(x$trials, x$prob, class(x))
```
```{r}
x
```

Note that the above code is not necessary to use this library, but it's a convenient way to store the 2 parameters of your specific binomial distribution.

### Gathering/plotting statisticss

Below, you can obtain and visualize the probability distribution and/or cumulative probability distribution of your specific binomial distribution.
```{r}
bin_distribution(x$trials, x$prob)
```
```{r}
plot(bin_distribution(x$trials, x$prob))
```
```{r}
bin_cumulative(x$trials, x$prob)
```
```{r}
plot(bin_cumulative(x$trials, x$prob))
```

For more statistics about your binomial distribution, use the generic method `summary`:
```{r}
summary(x)
```

Moreover, there some other basic functions available to you to calculate simple statistics of your binomial distribution:
```{r}
# calculates 5 choose 3
bin_choose(5, 3)

# calculates 5 choose 3, 5 choose 4
bin_choose(5, 3:4)
```
```{r}
# calculates the probability of 3 and 4 successes out of 5 trials
# with 50% chance of success on each trial
bin_probability(3:4, 5, 0.5)
```
```{r}
# simple statistics
bin_mean(trials=2, prob=0.5)
bin_variance(trials=2, prob=0.5)
bin_mode(trials=2, prob=0.5)
bin_skewness(trials=2, prob=0.5)
bin_kurtosis(trials=2, prob=0.5)
```

